### 2022-12-19 preface.tex
last polish of intro?

I also want to thank my friends and colleagues from the Epidemiology,
Biostatistics and Prevention Institute from the University of Zurich (in
alphabetical order): Ainesh, Alexandra, Annina, Charlotte, Babette, Bálint,
Beate, Beni,Eveline, Eva, Franscesca, Felix, Julia, Klaus, Kelly, Lucas, Lisa,
Luisa, Goscha, Manuela, Monika, Muriel, Manja, Maria, Marielena, Nadja, Ruedi,
Rachel, Sandra, Sona, Steffi, Torsten, and Ulrike. Another thanks goes to my
friends from the Department of Psychological Methods from the University of
Amsterdam (in alphabetical order): Adam, Alexander, Alexandra, Alessandra,
Angelika, Bruno, Don, František, Frederik, Jason, Johnny, Joris, Jill, Lukas,
Maarten, Michelle, Nora, Omid, Quentin, René, Serjan, Suzanne, and Ting. I also
want to thank my good friends from outside of academia (in alphabetical order):
Chronis, Dani, Eleftheria, Flo, Fabi, Giuachin, Mirela, and Peter. A special
thanks goes to Ada. Finally, I thank my family: Beni, Christa, Elisabeth,
Fabian, Harry, Markus, Maja, and Noemi for their support.

>>>>

I also want to thank my friends and colleagues from the Epidemiology,
Biostatistics and Prevention Institute from the University of Zurich (in
alphabetical order): Ainesh, Alexandra, Annina, Charlotte, Babette, Bálint,
Beate, Beni, Eveline, Eva, Franscesca, Felix, Julia, Klaus, Kelly, Lucas, Lisa,
Luisa, Goscha, Manuela, Monika, Muriel, Manja, Maria, Marielena, Nadja, Ruedi,
Rachel, Sandra, Sona, Steffi, Torsten, and Ulrike. Another thanks goes to my
friends from the Department of Psychological Methods from the University of
Amsterdam (in alphabetical order): Adam, Alexander, Alexandra, Alessandra,
Angelika, Bruno, Don, František, Frederik, Jason, Johnny, Joris, Jill, Lukas,
Maarten, Michelle, Nora, Omid, Quentin, René, Serjan, Suzanne, and Ting. I also
want to thank my good friends from outside of academia (in alphabetical order):
Chronis, Dani, Eleftheria, Flo, Fabi, Giuachin, Mirela, and Peter. A special
thanks goes to Ada. Finally, I thank my family: Beni, Christa, Elisabeth,
Fabian, Harry, Laurin, Markus, Maja, and Noemi for their support.
